\Large \textbf{ \includegraphics[height=\baselineskip]{title} \\ Project Proposal } \\ \vspace{0.025 in} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-04-27 proposal.tex
finish explain the attack

\section{What}
- Explain the attack
  - When/how were IDN introduced
  - Homograph letters
  - How to use this to the attackers advantage

@@

- Conclusion
  - Impact of the vulnerability based on empirical data and % of users still vulnerable

>>>>

\section{What}

- Explain the attack
  - When/how were IDN introduced
  - Homograph letters
  - How to use this to the attackers advantage

Domain name were designed to support ASCII character. Internationalized domain name(IDN) was proposed in December 1996 by Martin Dürst for the purpose of letting non-English speaking people use Internet without restriction[1]. The solution is to implement unicode mapping every character in different language to a unique number. Homograph letters, however, could be a potential vulnerability. For example, Cyrillic letter 'a' can look identical to Latin letter 'a'. Attackers can use the website "www.apple.com" where 'a' actually is a Cyrillic letter to attack users. In some other language, like Chinese, there exists many homographs between traditional Chinese and simplified Chinese.

@@

- Conclusion
  - Impact of the vulnerability based on empirical data and % of users still vulnerable
  - Possible solution for this vulnerability. How does company solve this problem.
